---
title: Practical Machine Learning Course Project
author: kwatanwa17
date: 23/9/2018
output: html_document
---
```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE, tidy = FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = TRUE, message = F, error = F, warning = F, comment = NA, fig.align = 'center', dpi = 100, tidy = F, cache.path = '.cache/', fig.path = 'fig/')

```

# Preproccesament

## Training data set

Load the data sets
```{r}
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
```

Load libraries
```{r}
library(dplyr)
```

### NA columm
```{r}
trainNA <- apply(training, 2, function(x) {
  sum(is.na(x))
})
training <- training[,trainNA == 0]
```

### blank columm
```{r}
trainBlank <- apply(training, 2, function(x) {
  sum(x%in%"")
})
training <- training[,trainBlank == 0]
```

### check class
```{r}
training_class <- sapply(training, class)
```

Factor class columm
```{r}
colnames(training[,training_class=="factor"])
```

We eliminate the following variables because they would not be useful to predict classe variable.

- X
- user_name
- cvtd_timestamp
- new_window

```{r}
training <- select(training, -c(X,user_name, cvtd_timestamp, new_window))
```

```{r}
summary(training)
```

## Test data set

Likewise, we clean the sample data set.
```{r}
testNA <- apply(testing, 2, function(x) {
  sum(is.na(x))
})
testing <- testing[,testNA==0]
testing <- select(testing, -c(X,user_name, cvtd_timestamp, new_window))
```

# Machine Learning
We select Linear Discriminant Analysis and Random Forest to classificate the classe variables.

Load the library
```{r}
library(caret)
```

## LDA

We use cross validation method.
```{r}
FitLDA <- train(classe ~., method = "lda", data = training,
                trControl = trainControl(method = "cv"))
FitLDA
```

The accuracy of LDA model is 0.7168995. 
```{r}
predLDA <- predict(FitLDA, training)
confusionMatrix(predLDA, training$classe)
```

We use this LDA model and pedict classes of the testing data set.
```{r}
predLDAtest <- predict(FitLDA, testing)
predLDAtest
```

## Random forest

Before we fit the data set to Random forest model, we need to prepare parallel processament.
```{r}
library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1) 
registerDoParallel(cluster)
fitControl <- trainControl(method = "cv",
                           number = 5,
                           allowParallel = TRUE)
```

Fit the training data to the model.
```{r}
FitRF <- train(classe ~., method = "rf", data = training,
                trControl = fitControl)
FitRF
```

This is the confusion matrix. As we can see, the classes are perfectly classificated.
```{r}
predRF <- predict(FitRF, training)
confusionMatrix(predRF, training$classe)
```

Precidt testing data.
```{r}
predRFtest <- predict(FitRF, testing)
predRFtest
```

Finally we compare two models' accordance.
```{r}
table(predLDAtest, predRFtest)
plot(predLDAtest)
plot(predRFtest)
```